\Large \bf One-Step, Three-Factor Authentication With Custom-Fit, In-Ear EEG

### 2017-02-10 paper.tex
new title
Removed ASSR stuff

%make title bold and 14 pt font (Latex default is non-bold, 16 pt)
\title{\Large \bf 3-Step, 1-Factor Authentication With Custom-Fit, In-Ear EEG}

@@

\subsection{Data Collection Protocol}
\label{sec:org2041857}
The data collection visit took approximately 90 minutes for set up and experiment execution. The OpenBCI system we used
allows for 8 channels of simultaneous recording, along with separate ground and reference channels.
Data was initially collected with the ground placed at the center of the forehead, and using the left
mastoid as reference, though we later re-referenced to the right mastoid channel. Each earpiece (shown in the image below) contains three channels: one placed on the helix, and two inside the canal - one front-facing and the other back-facing. The remaining
two channels were placed on the right mastoid for later re-referencing, and at approximately Fp1 (on the 
forehead above the left eye) for validating the data collected in the ears against a scalp-based measure. 
Before beginning the experiment, the data from each channel was visually inspected and participants were asked to
blink and clench their jaws to confirm that all channels were active and properly connected. Audio stimuli was delivered through small tubes in the earpieces opening into the ear canal.

@@

 After the completion of the experiment, a subset of participants completed a usability questionnaire asking about the ease of performing, level of engagement, perceived repeatability, and likeliness of using each task. The questionnaire also asked participants to rank the tasks overall from most to least favorite, as well as several open response questions regarding potential use cases of ear EEG and this method of authentication, level of comfort wearing the earpieces, and any other comments they chose to provide.
\section{Analysis}
\label{sec:org6c1a839}
\subsection{Validating the data {\bfseries\sffamily TODO (Update beyond pilot participants}}
\label{sec:org800f2bd}

In this section, we establish that the data we collected were EEG signals with relatively low noise. 
Using the pilot data from two participants, we were able to confirm the custom-fit earpieces are able to collect EEG
data using three tests: good impedances measured for the ear electrodes, alpha-band activity attenuation when a
participant's eyes were open versus closed, and the presence of a significant ASSR signal.

@@

Finally, for the ASSR test we calculated power spectra for data from the "Listen - ASSR" task. The audio stimulus used for this task is modulated 
at 40 Hz, which should, in turn, produce an EEG response visible in the data at 40 Hz. Strangely, in our tests we do see an ASSR spike but it is located 
around 74 Hz instead. While this has us somewhat perplexed about our stimulus, the purpose of this test was to ensure that the response seen in the ear channels 
matched the response seen from the Fp1 recordings, which is evident comparing the figures below.

\begin{figure}[h]
\centering
\includegraphics[width=0.5\textwidth]{figures/001_ASSR_Fp1.jpg}
\caption{Power spectrum for data collected from the Fp1 channel during 40 Hz ASSR stimulus. An ASSR spike is clearly visible, though not at 40 Hz where it was expected.}
\end{figure}

\begin{figure}[h]
  \centering
  \begin{minipage}[b]{0.45\textwidth}
    \includegraphics[width=\textwidth]{figures/001_ASSR_Left.jpg}
  \end{minipage}
  \hfill
  \begin{minipage}[b]{0.45\textwidth}
    \includegraphics[width=\textwidth]{figures/001_ASSR_Right.jpg}
  \end{minipage}
\caption{Power spectra for data collected from the earpiece channels during 40 Hz ASSR stimulus. Again, the spike is clearly visible though not at 40 Hz, however it 
does match the activity measured at Fp1.}
\end{figure}

@@

\subsection{Imposter attack}

@@

To explore this scenario, we chose one subject (subject 6), and referred to their report of chosen passsthoughts. We recorded spoofed passthoughts for two ``imposter'' subjects. One subject appeared in our initial pool performing their own passthoughts (subject 2), while the other subject did not appear in the initial pool, and thus was not included when training subject classifiers. (How well the imposters were able to spoof subject 6's passthought is an open question; see Discussion).

For each task, we ran the spoofed version of the task through the classifier trained on subject 6's task as the passthought.
None of the spoofed passthoughts were accepted, resulting in a 0\% FAR.

\subsection{{\bfseries\sffamily TODO} Usability}
\label{sec:org18d5968}

@@

Counter to our expectations, we found that referencing on the same side as the electrodes improves classification accuracy. This result implies that our tasks do not involve inter-hemispheric dynamics (if our tasks require symmetric neural activity, referencing to the other hemisphere would incorporate additional noise, explaining our finding). Since a single earpiece is more convenient from a usability and manufacturing standpoint, tasks with symmetric activity should be preferred in future work.

>>>>

%make title bold and 14 pt font (Latex default is non-bold, 16 pt)
\title{\Large \bf One-Step, Three-Factor Authentication With Custom-Fit, In-Ear EEG}

@@

\subsection{Data Collection Protocol}
\label{sec:org2041857}
The data collection visit took approximately 90 minutes for set up and experiment execution. The OpenBCI system we used
allows for 8 channels of simultaneous recording, along with separate ground and reference channels.
Data was initially collected with the ground placed at the center of the forehead, and using the left
mastoid as reference, though we later re-referenced to the right mastoid channel, so that our analysis reflects data from a single earpiece. Each earpiece (shown in the image below) contains three channels: one placed on the helix, and two inside the canal - one front-facing and the other back-facing. The remaining
two channels were placed on the right mastoid for later re-referencing, and at approximately Fp1 (on the 
forehead above the left eye) for validating the data collected in the ears against a scalp-based measure. 
Before beginning the experiment, the data from each channel was visually inspected and participants were asked to
blink and clench their jaws to confirm that all channels were active and properly connected. Audio stimuli was delivered through small tubes in the earpieces opening into the ear canal.

@@

 After the completion of the experiment, a subset of participants completed a usability questionnaire asking about the ease of performing, level of engagement, perceived repeatability, and likeliness of using each task. The questionnaire also asked participants to rank the tasks overall from most to least favorite, as well as several open response questions regarding potential use cases of ear EEG and this method of authentication, level of comfort wearing the earpieces, and any other comments they chose to provide.

\section{Analysis}
\label{sec:org6c1a839}
\subsection{Validating the data {\bfseries\sffamily TODO (Update beyond pilot participants}}
\label{sec:org800f2bd}

In this section, we establish that the data we collected were of a neural origin, and had relatively little noise. 
Using data from two participants, we were able to confirm the custom-fit earpieces are able to collect EEG
data using three tests: good impedances measured for the ear electrodes, and alpha-band activity attenuation when a
participant's eyes were open versus closed.

@@

@@

\section{Imposter attack}

@@

To explore this scenario, we chose one subject (subject 6), and referred to their report of chosen passsthoughts. One subject, drawn from the initial pool, \underline{...methods..}.
\underline{....results.....}

However, since this subject's data appeared in the initial pool, the classifier may have been trained on his or her recordings as negative examples. To explore the efficacy of an outsider spoofing recordings, we repeated the same protocol with a subject who did not appear in our initial set of subjects.
\underline{...results....}

% We recorded spoofed passthoughts for two ``imposter'' subjects. One subject appeared in our initial pool performing their own passthoughts (subject 2), while the other subject did not appear in the initial pool, and thus was not included when training subject classifiers. (How well the imposters were able to spoof subject 6's passthought is an open question; see Discussion).
% For each task, we ran the spoofed version of the task through the classifier trained on subject 6's task as the passthought. None of the spoofed passthoughts were accepted, resulting in a 0\% FAR.

\section{{\bfseries\sffamily TODO} Usability}

@@
